An upper bound to gas storage and delivery via pressure-swing adsorption in porous materials

### 2020-06-01 gas-adsorption/gas-ads-appendix.tex
the latest paper changes.

\begin{align}
    \frac{\delta D}{\delta \Vk} &= 0, \text{ if } \kvec\ne 0.
\end{align}
We note that this functional derivative may be non-zero for $\kvec=0$ because
we separately maximize with respect to the particular uniform potential $\V$.
This means that

\begin{align}
    \frac{\delta N_H}{\delta \Vk} &= \frac{\delta N_L}{\delta \Vk}
\end{align}
where $N_H$ and $N_L$ are the number of particles at the low and high pressure.

@@

\section{The real-substrate analog of $\V$ is $\gst$}
\label{sec:phi-is-delta-g}
\begin{figure}
    \centering
    \includegraphics[width=\columnwidth]{g_st_piston_2.png}
    \caption{Cartoon illustrating the definition of $\gst$ and a
      hypothetical experiment to measure it with a piston and
      removable barrier that separates two equal volumes, one with a
      porous material (bottom) and one with free space (top). The
      initial state (left) is a bulk gas phase at density $\rho$ and
      temperature $T$. An infinitely-thin, removable barrier separates
      the gas from the porous material (bottom). The barrier is then
      slowly removed, and the piston slowly pushes all gas molecules
      into the porous material in an isothermal process. The final
      state (right) is an adsorbed gas phase at density $\rho$ and
      temperature $T$.}
    \label{fig:delta-G-cartoon}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=0.95\columnwidth]{four-cases-pro}
    \caption{Two pairs of boxes containing gas with one of the pairs
    filled with MOF. One box of each sort has a density of gas $\rhofull$
    corresponding to $\pfull$ in the MOF system, while the other two boxes has
    gas density $\rhoempty$}
    \label{fig:delta-gst-maximum}
\end{figure}

\section{An upper bound when $\gst(\rho)$ is monotonic}\label{sec:monotonic}
Every MOF has a $\Delta g_\text{st}$ at $\pfull$ and $\pempty$ corresponding
to a full and empty density. The deliverable capacity of the MOF is equal to
the difference between the full and empty density. Examining
Fig.~\ref{fig:methane-gst}, we see that a significant variety of known
experimental $\Delta g_\text{st}$ curves are monotonic. Furthermore, our
qualitative argument in Section~\ref{sec:upper-bound} suggests that this
function \emph{should} monotonically increase for rigid substrates, as
increasing the density of gas causes some of the gas to reside in higher-energy
sites. If this is always the case, the deliverable capacity will always be
bounded by our theoretical upper bound, even for a value of $\V$ that is not
optimal.

To show this, we perform a thought experiment illustrated in
Fig.~\ref{fig:delta-gst-maximum}. We begin with two pairs of boxes containing
gas. Two of the boxes are filled with a MOF, and the other two have a uniform
potential energy $\V$. We imagine the two boxes at $\V$ as being empty
but at very low altitude where gravity provides a potential energy difference
(relative to the box with the MOF in it) of $\V$ to each gas molecule (perhaps
we are on Jupiter?). One box of each sort has a density of gas $\rhofull$
corresponding to $\pfull$ in the MOF system, while the other two boxes has gas
density $\rhoempty$.

We now consider what happens if we introduce a diffusive connection between two
boxes that are initially at the same density, for instance by connecting them
with a tube. If the chemical potential of the two boxes are equal, their
density will be unchanged, otherwise gas will flow into the box with lower
chemical potential. The difference in chemical potential is equal to the
difference

\begin{align}
   \gst(\rho) - \V &= \left(\mu_{\text{MOF}}(\rho) - \mu_{\text{gas}}(\rho)\right)
   - \left(\mu_{\V}(\rho) - \mu_{\text{gas}}(\rho)\right)
   \\
   &= \mu_{\text{MOF}}(\rho) - \mu_{\V}(\rho).
\end{align}
Thus if $\gst(\rhoempty) = \V$ then the ``empty'' containers will remain at
their initial density after they are connected. Thus, the deliverable capacity
of the MOF will be greater than the deliverable capacity of the model with
uniform potential $\V$ if and only if $\gst(\rhofull)<\V$, i.e. if $\gst(\rho)$
does \emph{not} monotonically increase. By the same token, if we consider the
case where $\gst(\rhofull) = \V$, then to achieve a greater deliverable
capacity than our model, the MOF must have less residual gas, which means that
gas must spontaneously flow from the low-density MOF to the box with potential
$\V$, which means that $\gst(\rhoempty)>\V$. Once again, exceeding our upper
bound requires a material with a $\gst(\rho)$ that does not increase
monotonically.

@@

\section{Cryogenic hydrogen storage}\label{sec:cryo-hydrogen}
\begin{figure}
    \centering
    \includegraphics[width=0.95\columnwidth]{hydrogen-77-n-vs-G}
    \caption{Deliverable capacity of hydrogen at 77\ K as a function of the attractive Gibbs free energy $\gst$. Experimental deliverable capacities for several MOFs (data from Ref.~\cite{garcia2018benchmark}) are shown along with the experimental values for $\gst$ at the empty and full pressures shown as $+$'s connected by a line.}
    \label{fig:hydrogen-77-D}
\end{figure}

>>>>

\begin{align}
    \frac{\delta D}{\delta \Vk} &= \mathbf{0}, \text{ if } \kvec\ne \mathbf{0}.
\end{align}
We note that this functional derivative may be non-zero for $\kvec=\mathbf{0}$ 
because we separately maximize with respect to the particular uniform potential 
$\V$. This means that

\begin{align}
    \frac{\delta N_\text{full}}{\delta \Vk} &= \frac{\delta N_\text{empty}}{\delta \Vk}
\end{align}
where $N_\text{full}$ and $N_\text{empty}$ are the number of particles at the full and empty pressure, respectively.

@@

\section{The real-substrate analog of $\V$ is $\gst$}
\label{sec:phi-is-delta-g}
\begin{figure}
    \centering
    \includegraphics[width=\columnwidth]{g_st_simple.pdf}
    \caption{Cartoon illustrating the definition of $\gst$. for a given adsorbent and gas, $\gst$=$\gst (\rho, T)$ is defined as the difference in chemical potential between the adsorbed gas system and bulk gas system when both exhibit the same density and temperature.}
    \label{fig:delta-G-cartoon}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=0.95\columnwidth]{four-cases-pro}
    \caption{Two pairs of two connected and equal volumes containing gas. In the top pair, the density of gas in each volume is $\rhofull$. In the bottom pair, the density of gas in each volume is $\rhoempty$. The two volumes on the left are packed with a porous material. The two volumes on the right offer a spatially uniform background potential energy $\V$ (our idealized substrate). A connection between the two volumes in each pair has a valve to allow flow of gas between them}
    \label{fig:delta-gst-maximum}
\end{figure}

\section{An upper bound when $\gst(\rho)$ is monotonic}\label{sec:monotonic}
Every MOF has a $\Delta g_\text{st}$ at $\pfull$ and $\pempty$ corresponding
to a full and empty density. The deliverable capacity of the MOF is equal to
the difference between the full and empty density. Examining
Fig.~\ref{fig:methane-gst}, we see that a significant variety of known
experimental $\Delta g_\text{st}$ curves are monotonic. Furthermore, our
qualitative argument in Section~\ref{sec:upper-bound} suggests that this
function \emph{should} monotonically increase for rigid substrates, as
increasing the density of gas causes some of the gas to reside in higher-energy
sites. If this is always the case, the deliverable capacity of a real material (with a non-spatially uniform potential) with a given $\gst$ at $\pfull$ or $\pempty$ is bounded below by the deliverable capacity in our idealized substrate with $\V=\gst$, even for a value of $\V$ that is not optimal

To show this, we perform a thought experiment illustrated in
Fig.~\ref{fig:delta-gst-maximum}. We begin with two pairs of volumes containing
gas. Within each pair, one volume is filled with a porous material, while the
other offers a uniform potential energy $\V$ (our idealized substrate). In the
first (second) pair, the density of gas in each volume is $\rhofull$
($\rhoempty$), corresponding to the density of gas adsorbed in the porous
material at $\pfull$ ($\pempty$).

We now consider what happens if we introduce a diffusive connection between a
volume of MOF and a volume with an idealized substrate that initially contain
the same density of gas, for instance by connecting them with a tube. If the
chemical potential of the two volumes are equal, their density will be
unchanged; otherwise gas will flow into the volume with lower chemical
potential. The difference in chemical potential is equal to the difference

\begin{align}
   \gst(\rho) - \V &= \left(\mu_{\text{MOF}}(\rho) - \mu_{\text{gas}}(\rho)\right)
   - \left(\mu_{\V}(\rho) - \mu_{\text{gas}}(\rho)\right)
   \\
   &= \mu_{\text{MOF}}(\rho) - \mu_{\V}(\rho).
\end{align}
where $\mu_{\text{MOF}}(\rho)$ and $\mu_{\V}(\rho)$ are the chemical potentials
of gas in the porous material and ideal substrate with potential $\V$, respectively. Thus if $\gst(\rhoempty) =
\V$ then the low-density containers will remain at their initial density after
they are connected. Thus, the deliverable capacity of the MOF will be greater
than the deliverable capacity of the ideal substrate with uniform potential $\V$ if and
only if $\gst(\rhofull)<\V$, i.e. if $\gst(\rho)$ does \emph{not} monotonically
increase, since the gas in the high-density system will flow from the ideal
substrate to the MOF. By the same token, if we consider the case where
$\gst(\rhofull) = \V$, then for the MOF to achieve a greater deliverable
capacity than the idealized substrate, the MOF must have less residual gas,
which means that gas must spontaneously flow from the low-density MOF to the
volume with potential $\V$, which means that $\gst(\rhoempty)>\V$. Once again,
exceeding our upper bound requires a material with a $\gst(\rho)$ that does not
increase monotonically.

@@

\section{Cryogenic hydrogen storage}\label{sec:cryo-hydrogen}
\begin{figure}
    \centering
    \includegraphics[width=0.95\columnwidth]{hydrogen-77-n-vs-G}
    \caption{Deliverable capacity of hydrogen at 77\ K as a function of the attractive Gibbs free energy $\gst$. Experimental deliverable capacities for several porous materials (data from Ref.~\cite{garcia2018benchmark}) are shown along with the experimental values for $\gst$ at the empty and full pressures shown as $+$'s connected by a line.}
    \label{fig:hydrogen-77-D}
\end{figure}

### 2020-06-01 gas-adsorption/gas-ads-body.tex
the latest paper changes.

\section{Introduction}
The transportation sector is dominantly powered by petroleum-based
fuels~\cite{davis2009transportation}. In the United Sates, it is responsible
for 36\% of energy-related carbon dioxide emissions \cite{useia} and $\sim$50,000
premature deaths per year associated with particulate matter and ozone
emissions~\cite{caiazzo2013air}. Natural gas and hydrogen (H$_2$) are
alternative transportation fuels that emit fewer/less pollutants than
petroleum-based fuels, and thus their widespread adoption could mitigate
climate change~\cite{mcglade2015geographical} and improve air quality for human
health. Further, as the finite global petroleum resources are declining
rapidly~\cite{sorrell2010global}, the development of technologies for the
widespread adoption of sustainable transportation fuels, such as hydrogen, is
critical.

@@

A promising approach to densify natural
gas~\cite{makal2012methane,mason2014evaluating} and
hydrogen~\cite{suh2011hydrogen,garcia2018benchmark} for vehicular storage at
room temperature is through physical adsorption in nanoporous
materials~\cite{schoedel2016role}. The internal surfaces of porous materials
attract gas molecules through van der Waals, electrostatic, etc. interactions
to achieve a higher adsorbed gas density than the bulk gas at the same
temperature and pressure, allowing for room temperature and lower-pressure
storage and alleviating many drawbacks of high-pressure, low-temperature
storage.

@@

To set realistic performance targets and optimally allocate research resources,
in this work, we present a theoretical framework that places an intrinsic upper
limit on the deliverable capacity of any gas in a rigid porous material and
uses as input the experimentally measured properties of the bulk gas. Our
extremum is provided by a substrate that offers a spatially uniform potential
energy field felt by the gas. Applying our framework to methane and hydrogen
gas, we find the US DOE deliverable capacity targets for natural gas and
hydrogen storage and delivery are theoretically possible, but sufficiently
close to the upper bound as to be impractical for any real porous material.
Optimistically, new paradigms outside the scope of applicability of our
theoretical framework, such as gas-induced structural transitions of the
material, hold promise for meeting these targets, as evidenced by flexible MOF
Co(bdp) which currently boasts the largest methane deliverable
capacity~\cite{mason2015methane}.

@@

G\'omez-Gualdr\'on \emph{et al.}~\cite{gomez2017impact} introduced a model that
accounted for gas-gas interactions via an intermolecular potential and
idealized the substrate in two different ways: (1) discrete adsorption sites
packed into an FCC lattice and (2) a volume endowed with a spatially uniform,
background potential energy field. According to molecular simulation of methane
adsorption, the ARPA-E deliverable capacity target of 315 L STP/L could be
reached in both of these idealized substrates. However, both models neglected
the space occupied by atoms of the porous material that are needed to endow the
adsorption sites/volume with the attractive potential energy and rely on a
molecular model for methane.

A third body of work incorporated both gas-gas interactions \emph{and} steric
interactions of the gas with the atoms of the porous material. Simulations of
methane adsorption in hundreds of thousands of explicit nanoporous crystal
structures---both real and hypothetical---suggested that the ARPA-E deliverable
capacity target is infeasible~\cite{simon2015materials}; the highest simulated
methane deliverable capacity was 196 cm$^3$~STP/cm$^3$. Confidence in this
conclusion rests upon (i) the accuracy of the intermolecular potentials
describing the molecular interactions and (ii) the sufficient sampling of
material space, i.e.\ that the structures considered are representative of the
set of possible materials. To further explore material space and address
sensitivity to the intermolecular potentials, scaling the Lennard-Jones
potential well depths of material atoms to model enhanced
interactions~\cite{gomez2014exploring}, placing Lennard-Jones spheres in a unit
cell randomly to form ``pseudo-materials''~\cite{kaija2018high}, and generating
fictitious potential energy fields via a generative adversarial network trained
on zeolite structures~\cite{lee2019predicting} all generated model substrates
that failed to meet the ARPA-E methane deliverable capacity target.

@@

\section{An upper bound on the deliverable capacity of a pure gas in a rigid porous material}\label{sec:upper-bound}
\begin{figure}
  \centering
  \includegraphics[width=\columnwidth]{methane-298-rho-mu}
  \caption{The density of bulk methane, the ideal gas, and adsorbed gas in several MOFs at 298\ K as a function of chemical potential (bottom axis) and pressure (top axis). The bulk methane density is from the National Institute of Standards and Technology (NIST)~\cite{nist}. The methane adsorption isotherms in the MOFs are experimental data from Ref.~\cite{mason2014evaluating, furukawa2009storage}.
  }
  \label{fig:density-vs-mu-ch4}
\end{figure}

@@

\begin{align}
    \rho_D(\V,T) &= \rho(\mufull,T) - \rho(\muempty,T),
    \label{eq:DofPhi}
    \\
    &= \rho_g(\mufull-\V,T) - \rho_g(\muempty-\V,T),
\end{align}
where $\mufull$ and $\muempty$ are the chemical potentials corresponding to the
pressures $\pfull$ and $\pempty$, respectively. Thus, $\rho_D$ for our
homogeneous substrate as a function of $\V$ is the difference between two
shifted versions of $\rho_g(\mu; T)$. Figure~\ref{fig:methane-298-D} shows the
two shifted bulk methane density curves and their difference. The horizontal
axis is the difference in molar Gibbs free energy, at fixed density and
temperature, between the gas within the substrate and the pure gas (\gst), which
is equal to $\V$ in our model, and is pressure-dependent in a real
crystal~(see Sec.~\ref{sec:phi-is-delta-g}). We see a potential $\V$ that maximizes the
deliverable capacity of our ideal substrate, balancing the need to maximize the
density at $\pfull$ against the need to minimize residual gas retained at
$\pempty$.

@@

An essential question is whether our idealized substrate, with spatially
uniform potential $\V_{opt}$ for the gas, places an upper bound on the
deliverable capacity in all rigid porous materials. In the SI (see
Section~\ref{sec:proof-extremum}), we show that our idealized substrate with
spatially uniform potential $\V_{opt}$ yields an \emph{extremum} of the
deliverable capacity over all possible \emph{static potential energy fields},
provided the gas does not crystallize at the temperature and in the density
range of interest. The potential energy field is \emph{static} if it is
unaffected by the presence of the gas; consequently, our model does not apply
to flexible materials that undergo gas-induced conformation
changes~\cite{schneemann2014flexible}. We next argue that this extremum is a
maximum by addressing two alternative possibilities: the extremum could turn
out to be (i) a saddle point or (ii) a local, rather than global, maximum.

Fig.~\ref{fig:methane-298-D} clearly shows that $\V_{opt}$ provides a maximum
$\rho_D$ over all \emph{spatially uniform}, static potential energy fields. To
qualitatively argue that the spatially uniform potential $\V_{opt}$ provides a
maximum deliverable capacity over \emph{all} (including non-spatially uniform)
static potential energy fields (a broader claim), consider a
non-spatially-uniform variation on $\V_{opt}$. The effect of
this variation is to reduce the deliverable capacity: At low adsorbed gas
densities, the lowest-energy positions will be preferentially occupied, while
at higher densities, the additional gas molecules will be forced into higher
energy locations. Thus, the mean attraction will be lowest at \pfull\ and
highest at \pempty. As a result, $\gst$ increases monotonically with
pressure. As shown in the SI (see Sec.~\ref{sec:monotonic}), this results in
the deliverable capacity of a non-uniform potential with a given $\gst$ at $\pfull$ or $pempty$ being lower than the
deliverable capacity of a uniform potential with $\V=\gst$. Thus, a spatially uniform potential gives the maximal
deliverable capacity amongst all static potential energy fields that give the
same $\gst$, and the \emph{optimal} uniform potential $\V_{opt}$ will yield a
greater deliverable capacity over any static, non-uniform potential.

@@

\begin{figure}
    \centering
    \includegraphics[width=0.95\columnwidth]{hydrogen-298-n-vs-G}
    \caption{Deliverable capacity of hydrogen at room temperature as a function of the attractive Gibbs free energy $|\gst|$.  Experimental deliverable capacities for several MOFs (data from Ref.~\cite{mason2014evaluating, garcia2018benchmark}) are shown along with the experimental values for $\gst$ at the empty and full pressures shown as $+$'s connected by a line.}
    \label{fig:hydrogen-298-D}
\end{figure}

@@

The second limitation of our proof arises in the assumption of a rigid
substrate. The rigid substrate acts as a static potential energy field for gas
molecules that is unchanged by the adsorption of gas. For most porous materials
this is a reasonable approximation, and this assumption is frequently made in
both the simulation and theory of porous materials~\cite{witman2017influence}.
However, there are cases where the substrate can provide a very strong
gas-density-dependent interaction through structural
flexibility~\cite{schneemann2014flexible}. A flagship example is MOF
Co(bdp)~\cite{choi2008broadly}, which possesses a wine-rack-like topology
capable of hinge motion. At low methane pressure, Co(bdp) adopts a collapsed,
nonporous state, but expands to a porous state and fills with gas at higher
pressures~\cite{mason2015methane}. This allows Co(bdp) to fully expel its
residual gas at low pressures. Our upper bound does not consider such material
effects, and thus flexible materials could have significantly higher
deliverable capacities.

>>>>

\section{Introduction}
The transportation sector is dominantly powered by petroleum-based
fuels~\cite{davis2009transportation}. In the United States, it is responsible
for 36\% of energy-related carbon dioxide emissions \cite{useia} and $\sim$50,000
premature deaths per year associated with particulate matter and ozone
emissions~\cite{caiazzo2013air}. Natural gas and hydrogen (H$_2$) are
alternative transportation fuels that emit fewer/less pollutants than
petroleum-based fuels, and thus their widespread adoption could mitigate
climate change~\cite{mcglade2015geographical} and improve air quality for human
health. Further, as the finite global petroleum resources are declining
rapidly~\cite{sorrell2010global}, the development of technologies for the
widespread adoption of sustainable transportation fuels, such as hydrogen, is
critical.

@@

A promising approach to densify natural
gas~\cite{makal2012methane,mason2014evaluating} and
hydrogen~\cite{suh2011hydrogen,garcia2018benchmark} for vehicular storage at
room temperature is through physical adsorption in nanoporous
materials~\cite{schoedel2016role}. The internal surfaces of porous materials
attract gas molecules through van der Waals, electrostatic, etc.\ interactions
to achieve a higher adsorbed gas density than the bulk gas at the same
temperature and pressure, allowing for room temperature and lower-pressure
storage and alleviating many drawbacks of high-pressure, low-temperature
storage.

@@

To set realistic performance targets and optimally allocate research resources,
in this work, we present a theoretical framework that places an intrinsic upper
limit on the deliverable capacity of any gas in a rigid porous material and
uses as input the experimentally measured properties of the bulk gas. Our
extremum is provided by a substrate that offers a spatially uniform potential
energy field felt by the gas. Applying our framework to methane and hydrogen
gas, we find the US DOE deliverable capacity targets for natural gas and
hydrogen storage and delivery are theoretically possible, but sufficiently
close to the upper bound as to be impractical for any real, rigid porous
material. Optimistically, new paradigms outside the scope of applicability of
our theoretical framework, such as gas-induced structural transitions of the
material, hold promise for meeting these targets, as evidenced by flexible MOF
Co(bdp) which currently boasts the largest methane deliverable
capacity~\cite{mason2015methane}.

@@

G\'omez-Gualdr\'on \emph{et al.}~\cite{gomez2017impact} introduced a model that
accounted for gas-gas interactions via an intermolecular potential and
idealized the substrate in two different ways: (1) discrete adsorption sites
packed into an FCC lattice and (2) a volume endowed with a spatially uniform,
background potential energy field. According to molecular simulation of methane
adsorption, the ARPA-E deliverable capacity target of 315 L STP/L could be
reached in both of these idealized substrates. However, both models (i)
neglected the space occupied by atoms of the porous material that are needed to
endow the adsorption sites/volume with the attractive potential energy and (ii)
rely on a molecular model for methane.

A third body of work incorporated both gas-gas interactions \emph{and} steric
interactions of the gas with the atoms of the porous material. Simulations of
methane adsorption in hundreds of thousands of explicit nanoporous crystal
structures---both real and hypothetical---suggested that the ARPA-E deliverable
capacity target is infeasible~\cite{simon2015materials}; the highest simulated
methane deliverable capacity was 196 cm$^3$~STP/cm$^3$. Confidence in this
conclusion rests upon (i) the accuracy of the intermolecular potentials
describing the molecular interactions and (ii) the sufficient sampling of
material space, i.e.\ that the structures considered are representative of the
set of possible materials. To further explore material space and address
sensitivity to the intermolecular potentials: scaling the Lennard-Jones
potential well depths of material atoms to model enhanced
interactions~\cite{gomez2014exploring}, placing Lennard-Jones spheres in a unit
cell randomly to form ``pseudo-materials''~\cite{kaija2018high}, and generating
fictitious potential energy fields via a generative adversarial network trained
on zeolite structures~\cite{lee2019predicting} all generated model substrates
that failed to meet the ARPA-E methane deliverable capacity target.

@@

\section{An upper bound on the deliverable capacity of a pure gas in a rigid porous material}\label{sec:upper-bound}
\begin{figure}
  \centering
  \includegraphics[width=\columnwidth]{methane-298-rho-mu}
  \caption{The density of bulk methane, the ideal gas, and adsorbed gas in several porous materials at 298\ K as a function of chemical potential (bottom axis) and pressure (top axis). The bulk methane density is from the National Institute of Standards and Technology (NIST)~\cite{nist}. The methane adsorption isotherms in the porous materials are experimental data from Ref.~\cite{mason2014evaluating, furukawa2009storage}.
  }
  \label{fig:density-vs-mu-ch4}
\end{figure}

@@

\begin{align}
    \rho_D(\V,T) &= \rho(\mufull,T) - \rho(\muempty,T),
    \label{eq:DofPhi}
    \\
    &= \rho_g(\mufull-\V,T) - \rho_g(\muempty-\V,T),
\end{align}
where $\mufull$ and $\muempty$ are the chemical potentials corresponding to the
pressures $\pfull$ and $\pempty$, respectively. Thus, $\rho_D$ for our
homogeneous substrate as a function of $\V$ is the difference between two
shifted versions of $\rho_g(\mu; T)$. Figure~\ref{fig:methane-298-D} shows the
two shifted bulk methane density curves and their difference. The horizontal
axis is the difference in molar Gibbs free energy, at fixed adsorbent density
and temperature, between the gas within the substrate and the pure gas (\gst),
which is equal to $\V$ in our model, and is pressure-dependent in a real
crystal~(see Sec.~\ref{sec:phi-is-delta-g}). We see a potential $\V$ that
maximizes the deliverable capacity of our ideal substrate, balancing the need
to maximize the density at $\pfull$ against the need to minimize residual gas
retained at $\pempty$.

@@

An essential question is whether our idealized substrate, with spatially
uniform potential $\V_{opt}$ for the gas, places an upper bound on the
deliverable capacity in all rigid porous materials. In
Section~\ref{sec:proof-extremum}, we show that our idealized substrate with
spatially uniform potential $\V_{opt}$ yields an \emph{extremum} of the
deliverable capacity over all possible \emph{static potential energy fields},
provided the gas does not crystallize at the temperature and in the density
range of interest. The potential energy field is \emph{static} if it is
unaffected by the presence of the gas; consequently, our model does not apply
to flexible materials that undergo gas-induced conformation
changes~\cite{schneemann2014flexible}. We next argue that this extremum is a
maximum by addressing two alternative possibilities: the extremum could turn
out to be (i) a saddle point or (ii) a local, rather than global, maximum.

Fig.~\ref{fig:methane-298-D} clearly shows that $\V_{opt}$ provides a maximum
$\rho_D$ over all \emph{spatially uniform}, static potential energy fields. To
qualitatively argue that the spatially uniform potential $\V_{opt}$ provides a
maximum deliverable capacity over \emph{all} (including non-spatially uniform)
static potential energy fields (a broader claim), consider a
non-spatially-uniform variation on $\V_{opt}$. The effect of
this variation is to reduce the deliverable capacity: At low adsorbed gas
densities, the lowest-energy positions will be preferentially occupied, while
at higher densities, the additional gas molecules will be forced into higher
energy locations. Thus, the mean attraction will be lowest at \pfull\ and
highest at \pempty. As a result, $\gst$ increases monotonically with
pressure. As shown in Sec.~\ref{sec:monotonic}, this results in
the deliverable capacity of a non-uniform potential with a given $\gst$ at $\pfull$ or $\pempty$ being lower than the
deliverable capacity of a uniform potential with $\V=\gst$. Thus, a spatially uniform potential gives the maximal
deliverable capacity amongst all static potential energy fields that give the
same $\gst$, and the \emph{optimal} uniform potential $\V_{opt}$ will yield a
greater deliverable capacity over any static, non-uniform potential.

@@

\begin{figure}
    \centering
    \includegraphics[width=0.95\columnwidth]{hydrogen-298-n-vs-G}
    \caption{Deliverable capacity of hydrogen at room temperature as a function of the attractive Gibbs free energy $|\gst|$.  Experimental deliverable capacities for several porous materials (data from Ref.~\cite{mason2014evaluating, garcia2018benchmark}) are shown along with the experimental values for $\gst$ at the empty and full pressures shown as $+$'s connected by a line.}
    \label{fig:hydrogen-298-D}
\end{figure}

@@

The second limitation of our proof arises in the assumption of a rigid
substrate. The rigid substrate acts as a static potential energy field for gas
molecules that is unchanged by the adsorption of gas. For most porous materials
this is a reasonable approximation, and this assumption is frequently made in
both the simulation and theory of porous materials~\cite{duren2009using}.
However, there are cases where the substrate can provide a very strong
gas-density-dependent interaction through structural
flexibility~\cite{schneemann2014flexible}. A flagship example is MOF
Co(bdp)~\cite{choi2008broadly}, which possesses a wine-rack-like topology
capable of hinge motion. At low methane pressure, Co(bdp) adopts a collapsed,
nonporous state, but expands to a porous state and fills with gas at higher
pressures~\cite{mason2015methane}. This allows Co(bdp) to fully expel its
residual gas at low pressures. Flexible materials could have significantly 
higher deliverable capacities, as our upper bound does not pertain to them.

### 2020-06-01 gas-adsorption/gas-ads.tex
added line numbering successfully.
made all changes in thesis after meeting and also changed fig in gas adsorption.
the latest paper changes.

\documentclass[letterpaper,twocolumn,amsmath,amssymb,nature]{revtex4-1}
\usepackage{graphicx} % Include figure files
\graphicspath{{figs/}}
\usepackage{color}
\usepackage{amsmath}
\usepackage{subfig}

\usepackage{lineno} % I added this to do line numbering

\usepackage{nicefrac} % Include for inline fractions
\usepackage{url}
\usepackage[hypertexnames=false]{hyperref}
\hypersetup{
    unicode=false,          % non-Latin characters in Acrobat’s bookmarks
    pdftoolbar=true,        % show Acrobat’s toolbar?
    pdfmenubar=true,        % show Acrobat’s menu?
    pdffitwindow=false,     % window fit to page when opened
    pdfstartview={FitH},    % fits the width of the page to the window
    pdftitle={Pommerenck Thesis},    % title
    pdfauthor={Jordan K. Pommerenck},     % author
    pdfsubject={Subject},   % subject of the document
    pdfcreator={Creator},   % creator of the document
    pdfproducer={Producer}, % producer of the document
    pdfkeywords={flat-histogram, Monte Carlo, Thesis}, % list of keywords
    pdfnewwindow=true,      % links in new PDF window
    colorlinks=true,       % false: boxed links; true: colored links
    linkcolor=black,          % color of internal links (change box color with linkbordercolor)
    citecolor=black,        % color of links to bibliography
    filecolor=magenta,      % color of file links
    urlcolor=cyan           % color of external links
}

@@

\begin{abstract}
Due to their low volumetric energy density at ambient conditions, both hydrogen
and natural gas are challenging to economically store onboard vehicles as
fuels~\cite{mason2014evaluating, sircar2002pressure}. One strategy to densify
these gases is to pack the fuel tank with a porous
material~\cite{schoedel2016role}. Metal-organic frameworks (MOFs) are tunable,
nanoporous materials with large internal surface areas and show considerable
promise for densifying gases~\cite{makal2012methane,mason2014evaluating,
suh2011hydrogen,garcia2018benchmark, schoedel2016role}. The US Department of
Energy (DOE) has set volumetric deliverable capacity
targets~\cite{simon2015materials, h2targetsDOE} which, if met, would help
enable commercial adoption of hydrogen/natural gas as transportation fuels.
Many have attempted to establish theoretical upper bounds on the deliverable
capacity via pressure-swing adsorption using simplified models of the
gas-substrate and gas-gas interaction~\cite{gomez2014exploring,
gomez2017impact, kaija2018high, lee2019predicting}; none have established a
rigorous upper bound on the deliverable capacity. Here, we present a
theoretical upper bound on the deliverable capacity of a rigid material via an
isothermal pressure-swing. To provide an extremum, we consider a substrate that
provides a spatially uniform potential energy field for the gas. Our bound is
unique in that it directly relies on experimentally measured properties of the
(real) bulk gas, without making approximations. We conclude that the goals set
by the US DOE for natural gas and hydrogen storage are theoretically possible,
but sufficiently close to the upper bound as to be impractical for any real
porous material. However, limitations to the scope of applicability of our
upper bound guide future material development efforts. Firstly, one could heat
the adsorbent to drive off residual gas trapped in the
adsorbent~\cite{gomez2014exploring}. Secondly, the fundamental physics of our
upper bound do not pertain to any material that changes its structure in
response to adsorbed gas, suggesting that flexible materials could still
satisfy the DOE targets~\cite{schneemann2014flexible, choi2008broadly,
mason2015methane}.

\end{abstract}

>>>>

\RequirePackage[mathlines]{lineno}
\documentclass[letterpaper,twocolumn,amsmath,amssymb,nature]{revtex4-2}
\setlength{\columnsep}{1cm}
\linenumbers

\usepackage{graphicx} % Include figure files
\graphicspath{{figs/}}
\usepackage{color}
\usepackage{amsmath}

%\usepackage{lineno} % I added this to do line numbering
\usepackage{subcaption}
\usepackage{nicefrac} % Include for inline fractions
\usepackage{url}
\usepackage[hypertexnames=false]{hyperref}
\hypersetup{
    unicode=false,          % non-Latin characters in Acrobat’s bookmarks
    pdftoolbar=true,        % show Acrobat’s toolbar?
    pdfmenubar=true,        % show Acrobat’s menu?
    pdffitwindow=false,     % window fit to page when opened
    pdfstartview={FitH},    % fits the width of the page to the window
    pdftitle={Pommerenck Thesis},    % title
    pdfauthor={Jordan K. Pommerenck},     % author
    pdfsubject={Subject},   % subject of the document
    pdfcreator={Creator},   % creator of the document
    pdfproducer={Producer}, % producer of the document
    pdfkeywords={flat-histogram, Monte Carlo, Thesis}, % list of keywords
    pdfnewwindow=true,      % links in new PDF window
    colorlinks=true,       % false: boxed links; true: colored links
    linkcolor=black,          % color of internal links (change box color with linkbordercolor)
    citecolor=black,        % color of links to bibliography
    filecolor=magenta,      % color of file links
    urlcolor=cyan           % color of external links
}

@@

\begin{linenomath}
\begin{abstract}
Due to their low volumetric energy density at ambient conditions, both hydrogen
and natural gas are challenging to economically store onboard vehicles as
fuels~\cite{mason2014evaluating, sircar2002pressure}. One strategy to densify
these gases is to pack the fuel tank with a porous
material~\cite{schoedel2016role}. Metal-organic frameworks (MOFs) are tunable,
nanoporous materials with large internal surface areas and show considerable
promise for densifying gases~\cite{makal2012methane,mason2014evaluating,
suh2011hydrogen,garcia2018benchmark, schoedel2016role}. The US Department of
Energy (DOE) has set volumetric deliverable capacity
targets~\cite{simon2015materials, h2targetsDOE} which, if met, would help
enable commercial adoption of hydrogen/natural gas as transportation fuels.
Many have attempted to establish theoretical upper bounds on the deliverable
capacity via pressure-swing adsorption using simplified models of the
gas-substrate and gas-gas interaction~\cite{gomez2014exploring,
gomez2017impact, kaija2018high, lee2019predicting}; none have established a
rigorous upper bound on the deliverable capacity. Here, we present a
theoretical upper bound on the deliverable capacity of a gas in a rigid
material via an isothermal pressure-swing. To provide an extremum, we consider
a substrate that provides a spatially uniform potential energy field for the
gas. Our bound is unique in that it directly relies on experimentally measured
properties of the (real) bulk gas, without making approximations. We conclude
that the goals set by the US DOE for room-temperature natural gas and hydrogen
storage are theoretically possible, but sufficiently close to the upper bound
as to be impractical for any real, rigid porous material. However, limitations
to the scope of applicability of our upper bound guide fuel tank design and
future material development. Firstly, one could heat the adsorbent to drive off
trapped, residual gas in the adsorbent~\cite{gomez2014exploring}. Secondly, the
physics of our upper bound do not pertain to any material that changes its
structure in response to adsorbed gas, suggesting that flexible materials could
still satisfy the DOE targets~\cite{schneemann2014flexible, choi2008broadly,
mason2015methane}.

\end{abstract}
\end{linenomath}
